%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {CDNTV/Technobox} % Organization
    {Porto Alegre, Brasil} % Location
    {Dec. 2019 - current} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Front-end development using the Yii and AdminLTE frameworks.}
        \item {Developed a video transcoding tool in Python, based on FFmpeg.}
        \item {Experience with Video Engineering: Over the Top TV, Video on Demand, HLS/RTMP streaming, CATV.}
        \item {Expertise in Streaming media, protocols, codecs, frame rate specs and mobile video specs.}
        \item {Experience with various equipment for receiving and transmitting channels such as decoders, encoders, transcoders and receivers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher} % Job title
    {Federal University of Rio Grande do Sul - UFRGS} % Organization
    {Porto Alegre, Brasil} % Location
    {Mar. 2018 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research grant and graduation work}
        \item {Internet stability under BGP stress}
        \item {Advised by Prof. Dr. Marinho Barcellos, co-advised by Prof. Me. Pedro de Botelho Marcos (FURG), in collaboration with Ignacio Castro (QMUL).}
        \item {I helped complete the Dynam-IX implementation on the Hyperledger Fabric platform and developed an Ethereum version written in Solidity.}
        \item {Developed a BGP route instability analysis platform with MRTparse \& Python.}
        \item {Experience with several tools, solutions and technologies such as Git, Blockchain \& BGP.}
      \end{cvitems}
    }

%---------------------------------------------------------


\end{cventries}
